Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/results.tex
Adding more to paper

The second metric for determining the appropriate grid size and mesh
resolution is through the correlation tensor and turbulence integral
length scale.  The two-point correlation tensor
$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
separation vector $\boldsymbol{\xi}$ is defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) = 
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as 
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}
and the overbar operator $\overline{(\bullet)}$ denotes time
averaging.  In the current study, we compute the horizontally averaged
correlation coefficient $\langle R_{ij}(\boldsymbol{\xi})\rangle$ by
sampling over multiple points at the $z$=20m height, typically 100-150
points, and averaging the result.  The longitudinal $\langle
R_{ij}(\boldsymbol{\xi})\rangle$ was calculated by looking at
separation vectors $\boldsymbol{\xi}$ in the streamwise direction
while the lateral $\langle R_{ij}(\boldsymbol{\xi})\rangle$ used
separation distances $\boldsymbol{\xi}$ which were orthogonal to the
wind direction on the same horizontal plane.

%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}%[hbt!]
  \centering
  \fxnote{remove AMR-Wind results from graphs}\\
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
  \caption{\label{fig:GridStudyRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{ij}(\boldsymbol{\xi})
    \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
    different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Similar conclusions can be drawn by examining the turbulent integral
length scale $L$.  This lengthscale can be calculated from $\langle
R_{ij}(\boldsymbol{\xi}) \rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{ij}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.  Based on this longitudinal
length scale, we also determined the overall domain size necessary for
stable ABL calculations.  A minimum domain of 750m $\times$ 750m in
the horizontal directions was used in all Nalu-Wind and AMR-Wind LES
calculations, which provided sufficient space for the largest
turbulent structures to develop and evolve without interference from
the boundaries or other structures.

@@

%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
    AMR-Wind and Nalu-Wind velocity profiles.  The dashed horizontal
    line corresponds to the measurement height z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles. The
    dashed horizontal line corresponds to the measurement height
    z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Wind spectra and turbulent correlation}

A comparison of the computed wind spectra $S_i(f)$ is shown in figure
\ref{fig:CompareAMRvsNaluSpectra}.

A comparison of the $R_{ij}$ correlation is shown in figure
\ref{fig:CompareAMRvsNaluRij}.

@@

  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
    and Nalu-Wind wind spectra at z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \caption{\label{fig:CompareAMRvsNaluRij}
    Comparison of AMR-Wind and Nalu-Wind $\langle R_{ij}
    \rangle$ correlation at z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Computational efficiency}
How much faster is AMR-Wind compared to Nalu-Wind?  \\
\fxnote{PUT SOME NUMBERS HERE FROM MIKE}

@@

@@

@@

%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
\begin{figure}[hbt!]
  \label{fig:ABLSpectra_AllZ}
  \centering
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
  \caption{Calculation of the wind spectra $S_i$ for LES of stable
    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
    vertical lines correspond to the maximum resolvable frequency
    $f_{max}$ according to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \label{fig:AllStabilityRij}
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{Calculation of the averaged longitudinal and lateral
    $R_{ij}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:StabilityStudyLscale} The calculated turbulent
  integral lengthscale for each of atmospheric stabilities} \centering
\begin{tabular}{ccccc}
  \hline
  Stability   & Wind speed & Longitudinal L [m] & Lateral L [m] \\
  \hline
  Stable      &   5 m/s  & 0.0           & 0.0        \\
  Stable      &  10 m/s  & 0.0           & 0.0        \\
  Stable      &  15 m/s  & 0.0           & 0.0        \\
  Neutral     &   5 m/s  & 110.435741    & 15.245327  \\
  Neutral     &  10 m/s  & 165.398368    & 20.634052  \\
  Neutral     &  15 m/s  & 184.081967    & 22.961169  \\
  Unstable    &   5 m/s  & 187.868710    & 270.538753 \\
  Unstable    &  10 m/s  & 177.457502    & 215.027457 \\
  Unstable    &  15 m/s  & 263.475309    & 67.999898  \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The second metric for determining the appropriate grid size and mesh
resolution is through the correlation tensor and turbulence integral
length scale.  The two-point correlation tensor
$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
separation vector $\boldsymbol{\xi}$ is defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) = 
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as 
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}
and the overbar operator $\overline{(\bullet)}$ denotes time
averaging.  In the current study, we compute the horizontally averaged
correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
sampling over multiple points at the $z$=20m height, typically 100-150
points, and averaging the result.  The longitudinal $\langle
R_{11}(\boldsymbol{\xi})\rangle$ was calculated by looking at
separation vectors $\boldsymbol{\xi}$ in the streamwise direction
while the lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$ used
separation distances $\boldsymbol{\xi}$ which were orthogonal to the
wind direction on the same horizontal plane.

%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}%[hbt!]
  \centering
  \fxnote{remove AMR-Wind results from graphs}\\
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
  \caption{\label{fig:GridStudyRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
    \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
    different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Similar conclusions can be drawn by examining the turbulent integral
length scale $L$.  This lengthscale can be calculated from $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.  Based on this longitudinal
length scale, we also determined the overall domain size necessary for
stable ABL calculations.  A minimum domain of 750m $\times$ 750m in
the horizontal directions was used in all Nalu-Wind and AMR-Wind LES
calculations, which provided sufficient space for the largest
turbulent structures to develop and evolve without interference from
the boundaries or other structures.

@@

%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
    AMR-Wind and Nalu-Wind velocity profiles for the stable 5 m/s
    boundary layer. The dashed horizontal line corresponds to the
    measurement height z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Wind spectra and turbulent correlation}

In addition to the mean profiles described above, we also examined the
wind spectra and turbulent correlation statistics from both AMR-Wind
and Nalu-Wind for the stable 5m/s case.  A comparison of the computed
wind spectra $S_i(f)$ from both LES codes is shown in figure
\ref{fig:CompareAMRvsNaluSpectra}.  At low frequencies, both AMR-Wind
and Nalu-Wind predict similar spectral behavior, and both codes
predict relatively similar spectral peaks for the $S_v$ and $S_w$
spectra.  For the longitudinal spectra $S_u$, however, AMR-wind
predicts a slightly lower the peak amplitude than Nalu-Wind.

A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
correlation coefficient is shown in figure
\ref{fig:CompareAMRvsNaluRij}.

@@

  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
    and Nalu-Wind wind spectra at z=20m for the stable 5 m/s boundary
    layer. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \caption{\label{fig:CompareAMRvsNaluRij}
    Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
    \rangle$ correlation at z=20m. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Computational efficiency}
How much faster is AMR-Wind compared to Nalu-Wind?  \\
\fxnote{PUT SOME NUMBERS HERE FROM MIKE}

@@

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{cccccc}
  \hline
  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  L \\
  \hline
  AMRWind & 5m/s      & 0.048255 &  0.165552 &  0.157399  & 52.512434 \\
  AMRWind & 10m/s     & 0.050580 &  0.160337 &  0.318941  &  57.233491 \\
  AMRWind & 15m/s     & 0.055034 &  0.118190 &  0.510645  & 131.341634 \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \label{fig:CompareAMRallWS}
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{Calculation of the wind spectra $S_i$ for LES of stable
    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
    vertical lines correspond to the maximum resolvable frequency
    $f_{max}$ according to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% Stable spectra, all Z figure %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
\begin{figure}[hbt!]
  \label{fig:ABLSpectra_AllZ}
  \centering
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
  \caption{Calculation of the wind spectra $S_i$ for LES of stable
    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
    vertical lines correspond to the maximum resolvable frequency
    $f_{max}$ according to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \label{fig:AllStabilityRij}
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{Calculation of the averaged longitudinal and lateral
    $R_{11}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% All stability, turbulent L figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \label{fig:AllStabilityLengthscale}
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
  \caption{Calculation of the averaged longitudinal and lateral
    lengthscale at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% %%%%%%%%%%%%%%% All stability: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%
%% % see  Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb
%% \begin{table}
%% \caption{\label{tab:StabilityStudyLscale} The calculated turbulent
%%   integral lengthscale for each of atmospheric stabilities} \centering
%% \begin{tabular}{ccccc}
%%   \hline
%%   Stability   & Wind speed & Longitudinal L [m] & Lateral L [m] \\
%%   \hline
%%   Stable      &   5 m/s  & 0.0           & 0.0        \\
%%   Stable      &  10 m/s  & 0.0           & 0.0        \\
%%   Stable      &  15 m/s  & 0.0           & 0.0        \\
%%   Neutral     &   5 m/s  & 110.435741    & 15.245327  \\
%%   Neutral     &  10 m/s  & 165.398368    & 20.634052  \\
%%   Neutral     &  15 m/s  & 184.081967    & 22.961169  \\
%%   Unstable    &   5 m/s  & 187.868710    & 270.538753 \\
%%   Unstable    &  10 m/s  & 177.457502    & 215.027457 \\
%%   Unstable    &  15 m/s  & 263.475309    & 67.999898  \\
%% \hline
%% \end{tabular}
%% \end{table}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
